Stable Hot Spot Analysis (Draft)

### 2017-06-15 paper-main.tex
updated images
added spacing to some images
Updated images to my imagination
Updated ref to images

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-1}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-2}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
\subsection{Impact of Aggregation level}
Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. We fix the aggregation and use it as x-axis. This allows us to examine the impact the resolution of a data set has on the results and allow us indirectly to reduce the computational effort on future computations by using the maximal aggregation as useful.
The results can seen in figure ~\ref{fig:SoHZoom} and ~\ref{fig:DownwardZoom}.
First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for zoom}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohup-1}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for zoom}
    \includegraphics[width=\linewidth]{images/gen-zoom-sohdown-1}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{SoH zoom}
  \label{fig:Zoom}
\end{figure}

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward for blur}
    \includegraphics[width=\linewidth]{images/SoHUpBlur}
    \label{fig:UpwardBlur}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward for blur}
    \includegraphics[width=\linewidth]{images/SoHDownBlur}
    \label{fig:DownwardBlur}
  \end{subfigure}
  \caption{SoH blur}
  \label{fig:Blur}
\end{figure}

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{
      Aggregation levels computed from original raster (log scale)
    }\\
    \hline
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
  \end{tabular}

%  \includegraphics[width=.45\linewidth]{images/gen-???}
%  \hspace{1em}
%  \includegraphics[width=.45\linewidth]{images/gen-???}

  \caption{
    This image shows all aggregation levels for G* and Focal G* together 
    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
  }
\end{figure*}

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
  \end{tabular}

%  \includegraphics[width=.45\linewidth]{images/gen-???}
%  \hspace{1em}
%  \includegraphics[width=.45\linewidth]{images/gen-???}

  \caption{
    This image shows all aggregation levels for G* and Focal G* together 
    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
  }
\end{figure*}

\section{Conclusions and Future Work} \label{sec:Conclusion}
In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. We validate the result from \ref{TODO last paper} with a real world 
dataset an with a larger dataset. The dataset was only one month projected in one raster. 
We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
is higher.
Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
Therefore F should be not less than 65x65. 
If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
has the least influence if $G^*$ or Focal $G^*$ performe better.
We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
it performes better, but this is beyond the scope of this work.

>>>>

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-1}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-2}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
\subsection{Impact of Aggregation level}
Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. 
We fix the aggregation and use it as x-axis. This allows us to examine the impact
the resolution of a data set has on the results and allow us indirectly to reduce the 
computational effort on future computations by using the maximal aggregation as useful.
The results can seen in figure ~\ref{fig:SoHZoom}.
First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.

@@

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{
      Aggregation levels computed from original raster (log scale)
    }\\
    \hline
    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\
    \includegraphics[width=4.6em]{images/gen-rawdata-1}&
    \includegraphics[width=4.6em]{images/gen-rawdata-2}&
    \includegraphics[width=4.6em]{images/gen-rawdata-3}&
    \includegraphics[width=4.6em]{images/gen-rawdata-4}&
    \includegraphics[width=4.6em]{images/gen-rawdata-5}&
    \includegraphics[width=4.6em]{images/gen-rawdata-6}&
    \includegraphics[width=4.6em]{images/gen-rawdata-7}&
    \includegraphics[width=4.6em]{images/gen-rawdata-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed from multiple aggregation levels} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed from multiple aggregation levels} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
  \end{tabular}

  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohup-1}
  \hspace{1em}
  \includegraphics[width=.45\linewidth]{images/gen-zoom-sohdown-1}
%  \includegraphics[width=.45\linewidth]{images/gen-???}
%  \hspace{1em}
%  \includegraphics[width=.45\linewidth]{images/gen-???}

  \caption{
    This image shows all aggregation levels for G* and Focal G* together 
    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
  }
  \label{fig:Zoom}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* computed using different weight matrix sizes} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* computed using different weight matrix sizes} \\
    \hline
    \vspace*{2mm}
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-blur-focalgstar-8}
  \end{tabular}

  \includegraphics[width=.45\linewidth]{images/gen-blur-sohdown-1}
  \hspace{1em}
  \includegraphics[width=.45\linewidth]{images/gen-blur-sohup-1}

  \caption{
    This image shows different weight matrix sizes for G* and Focal G* together 
    with two metrics -- $SoH^\uparrow$ and $SoH^\downarrow$.
  }
  \label{fig:Blur}
\end{figure*}

\begin{figure*}[htp]
  \centering

  \begin{subfigure}{.35\linewidth}
    \caption{G* clustering difference}
    \includegraphics[width=\linewidth]{images/gen-metric-example-1}
    \label{fig:ClustDiffGstar}
  \end{subfigure}
  \hspace{3em}
  \begin{subfigure}{.35\linewidth}
    \caption{Focal G* clustering difference}
    \includegraphics[width=\linewidth]{images/gen-metric-example-2}
    \label{fig:ClustDiffFocalGstar}
  \end{subfigure}

  \caption{
    Example clustering for G* and Focal G* used as a input for SoH computation.
  }
\end{figure*}

\section{Conclusions and Future Work} \label{sec:Conclusion}
In this work, we compared the Getis-Ord statistic with Focal Getis-Ord statisitic. 
We validate the result from \ref{SoH-GI-Forum} with a real world 
dataset an with a larger dataset. The dataset was only one month projected in one raster. 
We examined further parameters and evaluated that $G^*$ and Focal $G^*$ performe better if the weight
is higher.
Our results indicate a high Focal range for the upward property and a maximum of 65x65 for the downward property.
Therefore F should be not less than 65x65. 
If we calculate the SoH for the zoom level, Getis-Ord leads to better results. In general the zoom level 
has the least influence if $G^*$ or Focal $G^*$ performe better.
We assume that if Focal $G^*$ has a different focal size for a different zoom level, 
it performes better, but this is beyond the scope of this work.
